\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

In the HD-SNN model, each neuron $\postsynaddr \in \postsynaddrspace$ connects to presynaptic afferent neurons from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses. Each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. Scanning all neurons $\postsynaddr$, we thus define the full set of $\Nsyn$ synapses, 
as $\synapse = \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn)\}_{\ranksyn \in [1,\Nsyn]}$, where each synapse is associated to a presynaptic address $\presynaddr_\ranksyn$, a postsynaptic address $\postsynaddr_\ranksyn$, a weight $\synapticweight_\ranksyn$, and a delay $\synapticdelay_\ranksyn$. This defines the full connectivity of the HD-SNN model (\seeFig{izhikevich}-\textit{(Right)} for an illustration).

>>>>

In the HD-SNN model, each neuron $\postsynaddr \in \postsynaddrspace$ connects to presynaptic afferent neurons from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses. Each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact the same afferent neuron with different delays through different synaptic connections. Scanning all neurons $\postsynaddr$, we thus define the full set of $\Nsyn$ synapses, 
as $\synapse = \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn)\}_{\ranksyn \in [1,\Nsyn]}$, where each synapse is associated to a presynaptic address $\presynaddr_\ranksyn$, a postsynaptic address $\postsynaddr_\ranksyn$, a weight $\synapticweight_\ranksyn$, and a delay $\synapticdelay_\ranksyn$. This defines the full connectivity of the HD-SNN model (\seeFig{izhikevich}-\textit{(Right)} for an illustration of the connectivity of one neuron with synaptic weights and delays).
